---
title: Plot.fig2.AT.mutation.vs.dose
author: "Akira Hirao"
date: "`r Sys.Date()`"
output:
  md_document:
    toc: true
    variant: markdown_github
  html_document:
    toc: true
---


-----


## Loading packages

```{r message = FALSE, warning = FALSE, echo = TRUE}
library(ggplot2)
library(stringr)
library(MASS)
library(glmmML)
library(lme4)
library(tidyverse)
library(nlstools)
library(ggforce)
library(grid)
library(AER)
library(pscl)
```

## Loading data set

```{r message = FALSE, warning = FALSE, echo = TRUE}
AT.all.mutations <- read.csv("../M2.mutations.full.list.csv",header=T)
AT_all_mutations <- read_csv("../M2.mutations.full.list.csv")
```

## Data preprocessing

```{r message = FALSE, warning = FALSE, echo = TRUE}
sample.vec <- c(sort(unique(AT.all.mutations$Sample1)))
AT.all.mutations$Sample1 <- factor(AT.all.mutations$Sample1, levels=sample.vec)
AT.all.mutations$Sample2 <- factor(AT.all.mutations$Sample2, levels=sample.vec)
AT.all.mutations$Sample3 <- factor(AT.all.mutations$Sample3, levels=sample.vec)
AT_all_mutations$Sample1 <- factor(AT_all_mutations$Sample1, levels=sample.vec)
AT_all_mutations$Sample2 <- factor(AT_all_mutations$Sample2, levels=sample.vec)
AT_all_mutations$Sample3 <- factor(AT_all_mutations$Sample3, levels=sample.vec)

AT.all.family <- subset(AT.all.mutations, AT.all.mutations$Sample2!="NA")
AT_all_family <- AT_all_mutations %>% filter(Sample2!="NA")

AT.all.sbs <- subset(AT.all.mutations, AT.all.mutations$Type=="SBS")
AT.all.indel <- subset(AT.all.mutations, AT.all.mutations$Type!="SBS")
AT.all.insertion <- subset(AT.all.mutations, AT.all.mutations$Type=="Insertion")
AT.all.deletion <- subset(AT.all.mutations, AT.all.mutations$Type=="Deletion")
AT_all_sbs <- AT_all_mutations %>% filter(Type=="SBS")
AT_all_indel <- AT_all_mutations %>% filter(Type!="SBS")
AT_all_insertion <- AT_all_mutations %>% filter(Type=="Insertion")
AT_all_deletion <- AT_all_mutations %>% filter(Type=="Deletion")


No_mutations_per_sample <- tapply(rep(AT_all_mutations$Chr,3), c(AT_all_mutations$Sample1,AT_all_mutations$Sample2,AT_all_mutations$Sample3), length)
No_mutations_per_sample[is.na(No_mutations_per_sample)] <- 0

No_family_mutations_per_sample <- tapply(rep(AT_all_family$Chr,3), c(AT_all_family$Sample1,AT_all_family$Sample2,AT_all_family$Sample3), length)
No_family_mutations_per_sample[is.na(No_family_mutations_per_sample)] <- 0

No_homo_mutations_per_sample <- tapply(c(AT_all_mutations$Chr[AT.all.mutations$Zygosity1=="homo"],AT_all_mutations$Chr[AT.all.mutations$Zygosity2=="homo"],AT_all_mutations$Chr[AT.all.mutations$Zygosity3=="homo"]), c(AT_all_mutations$Sample1[AT.all.mutations$Zygosity1=="homo"],AT_all_mutations$Sample2[AT.all.mutations$Zygosity2=="homo"],AT_all_mutations$Sample3[AT.all.mutations$Zygosity3=="homo"]), length)
No_homo_mutations_per_sample[is.na(No_homo_mutations_per_sample)] <- 0

No_hetero_mutations_per_sample <- tapply(c(AT_all_mutations$Chr[AT.all.mutations$Zygosity1=="hetero"],AT_all_mutations$Chr[AT.all.mutations$Zygosity2=="hetero"],AT_all_mutations$Chr[AT.all.mutations$Zygosity3=="hetero"]), c(AT_all_mutations$Sample1[AT.all.mutations$Zygosity1=="hetero"],AT_all_mutations$Sample2[AT.all.mutations$Zygosity2=="hetero"],AT_all_mutations$Sample3[AT.all.mutations$Zygosity3=="hetero"]), length)
No_hetero_mutations_per_sample[is.na(No_hetero_mutations_per_sample)] <- 0

No_sbs_per_sample <- tapply(rep(AT_all_sbs$Chr,3), c(AT_all_sbs$Sample1,AT_all_sbs$Sample2,AT_all_sbs$Sample3), length)
No_sbs_per_sample[is.na(No_sbs_per_sample)] <- 0

No_indel_per_sample <- tapply(rep(AT_all_indel$Chr,3), c(AT_all_indel$Sample1,AT_all_indel$Sample2,AT_all_indel$Sample3), length)
No_indel_per_sample[is.na(No_indel_per_sample)] <- 0

No_insertion_per_sample <- tapply(rep(AT_all_insertion$Chr,3), c(AT_all_insertion$Sample1,AT_all_insertion$Sample2,AT_all_insertion$Sample3), length)
No_insertion_per_sample[is.na(No_insertion_per_sample)] <- 0

No_deletion_per_sample <- tapply(rep(AT_all_deletion$Chr,3), c(AT_all_deletion$Sample1,AT_all_deletion$Sample2,AT_all_deletion$Sample3), length)
No_deletion_per_sample[is.na(No_deletion_per_sample)] <- 0


No.mutations.per.sample1 <- tapply(AT.all.mutations$Chr, AT.all.mutations$Sample1, length)
No.mutations.per.sample2 <- tapply(AT.all.mutations$Chr, AT.all.mutations$Sample2, length)
No.mutations.per.sample3 <- tapply(AT.all.mutations$Chr, AT.all.mutations$Sample3, length)
No.mutations.per.sample1[is.na(No.mutations.per.sample1)] <- 0
No.mutations.per.sample2[is.na(No.mutations.per.sample2)] <- 0
No.mutations.per.sample3[is.na(No.mutations.per.sample3)] <- 0
No.mutations.per.sample <- No.mutations.per.sample1 + No.mutations.per.sample2 + No.mutations.per.sample3

No.family.mutations.per.sample1 <- tapply(AT.all.family$Chr,AT.all.family$Sample1, length)
No.family.mutations.per.sample2 <- tapply(AT.all.family$Chr,AT.all.family$Sample2, length)
No.family.mutations.per.sample3 <- tapply(AT.all.family$Chr,AT.all.family$Sample3, length)
No.family.mutations.per.sample1[is.na(No.family.mutations.per.sample1)] <- 0
No.family.mutations.per.sample2[is.na(No.family.mutations.per.sample2)] <- 0
No.family.mutations.per.sample3[is.na(No.family.mutations.per.sample3)] <- 0
No.fammily.mutations.per.sample <- No.family.mutations.per.sample1 + No.family.mutations.per.sample2 + No.family.mutations.per.sample3

No.homo.mutations.per.sample1 <- tapply(AT.all.mutations$Chr[AT.all.mutations$Zygosity1=="homo"], AT.all.mutations$Sample1[AT.all.mutations$Zygosity1=="homo"], length)
No.homo.mutations.per.sample2 <- tapply(AT.all.mutations$Chr[AT.all.mutations$Zygosity2=="homo"], AT.all.mutations$Sample2[AT.all.mutations$Zygosity2=="homo"], length)
No.homo.mutations.per.sample3 <- tapply(AT.all.mutations$Chr[AT.all.mutations$Zygosity3=="homo"], AT.all.mutations$Sample3[AT.all.mutations$Zygosity3=="homo"], length)
No.homo.mutations.per.sample1[is.na(No.homo.mutations.per.sample1)] <- 0
No.homo.mutations.per.sample2[is.na(No.homo.mutations.per.sample2)] <- 0
No.homo.mutations.per.sample3[is.na(No.homo.mutations.per.sample3)] <- 0
No.homo.mutations.per.sample <- No.homo.mutations.per.sample1 + No.homo.mutations.per.sample2 + No.homo.mutations.per.sample3

No.hetero.mutations.per.sample1 <- tapply(AT.all.mutations$Chr[AT.all.mutations$Zygosity1=="hetero"], AT.all.mutations$Sample1[AT.all.mutations$Zygosity1=="hetero"], length)
No.hetero.mutations.per.sample2 <- tapply(AT.all.mutations$Chr[AT.all.mutations$Zygosity2=="hetero"], AT.all.mutations$Sample2[AT.all.mutations$Zygosity2=="hetero"], length)
No.hetero.mutations.per.sample3 <- tapply(AT.all.mutations$Chr[AT.all.mutations$Zygosity3=="hetero"], AT.all.mutations$Sample3[AT.all.mutations$Zygosity3=="hetero"], length)
No.hetero.mutations.per.sample1[is.na(No.hetero.mutations.per.sample1)] <- 0
No.hetero.mutations.per.sample2[is.na(No.hetero.mutations.per.sample2)] <- 0
No.hetero.mutations.per.sample3[is.na(No.hetero.mutations.per.sample3)] <- 0
No.hetero.mutations.per.sample <- No.hetero.mutations.per.sample1 + No.hetero.mutations.per.sample2 + No.hetero.mutations.per.sample3

No.sbs.per.sample1 <- tapply(AT.all.sbs$Chr, AT.all.sbs$Sample1, length)
No.sbs.per.sample2 <- tapply(AT.all.sbs$Chr, AT.all.sbs$Sample2, length)
No.sbs.per.sample3 <- tapply(AT.all.sbs$Chr, AT.all.sbs$Sample3, length)
No.sbs.per.sample1[is.na(No.sbs.per.sample1)] <- 0
No.sbs.per.sample2[is.na(No.sbs.per.sample2)] <- 0
No.sbs.per.sample3[is.na(No.sbs.per.sample3)] <- 0
No.sbs.per.sample <- No.sbs.per.sample1 + No.sbs.per.sample2 + No.sbs.per.sample3

No.indel.per.sample1 <- tapply(AT.all.indel$Chr, AT.all.indel$Sample1, length)
No.indel.per.sample2 <- tapply(AT.all.indel$Chr, AT.all.indel$Sample2, length)
No.indel.per.sample3 <- tapply(AT.all.indel$Chr, AT.all.indel$Sample3, length)
No.indel.per.sample1[is.na(No.indel.per.sample1)] <- 0
No.indel.per.sample2[is.na(No.indel.per.sample2)] <- 0
No.indel.per.sample3[is.na(No.indel.per.sample3)] <- 0
No.indel.per.sample <- No.indel.per.sample1 + No.indel.per.sample2 + No.indel.per.sample3

No.insertion.per.sample1 <- tapply(AT.all.insertion$Chr, AT.all.insertion$Sample1, length)
No.insertion.per.sample2 <- tapply(AT.all.insertion$Chr, AT.all.insertion$Sample2, length)
No.insertion.per.sample3 <- tapply(AT.all.insertion$Chr, AT.all.insertion$Sample3, length)
No.insertion.per.sample1[is.na(No.insertion.per.sample1)] <- 0
No.insertion.per.sample2[is.na(No.insertion.per.sample2)] <- 0
No.insertion.per.sample3[is.na(No.insertion.per.sample3)] <- 0
No.insertion.per.sample <- No.insertion.per.sample1 + No.insertion.per.sample2 + No.insertion.per.sample3

No.deletion.per.sample1 <- tapply(AT.all.deletion$Chr, AT.all.deletion$Sample1, length)
No.deletion.per.sample2 <- tapply(AT.all.deletion$Chr, AT.all.deletion$Sample2, length)
No.deletion.per.sample3 <- tapply(AT.all.deletion$Chr, AT.all.deletion$Sample3, length)
No.deletion.per.sample1[is.na(No.deletion.per.sample1)] <- 0
No.deletion.per.sample2[is.na(No.deletion.per.sample2)] <- 0
No.deletion.per.sample3[is.na(No.deletion.per.sample3)] <- 0
No.deletion.per.sample <- No.deletion.per.sample1 + No.deletion.per.sample2 + No.deletion.per.sample3

treat <- c(rep("Control",length=9),rep("Low",length=9),rep("Middle",length=9),rep("High",length=9))
gray <- c(rep(0,length=9),rep(0.4,length=9),rep(1.4,length=9),rep(2.0,length=9))
Group <- c(rep("Group1",18),rep("Group2",18))
Group <- factor(Group, levels=c("Group1", "Group2"))
Accumurate.gray <- gray*60
Accumurate.gray.revised <- c(rep(0,length=9),rep(23,length=9),rep(80,length=9),rep(114,length=9))
family <-c(rep("A01",length=3),rep("A02",length=3),rep("A03",length=3),rep("A11",length=3),rep("A12",length=3),rep("A13",length=3),rep("A21",length=3),rep("A22",length=3),rep("A23",length=3),rep("A31",length=3),rep("A32",length=3),rep("A33",length=3))

mutation.count.frame <- data.frame(SampleID = sample.vec, Family = family,
	Treat = treat, Gray = gray, TotalGray = Accumurate.gray,
	Mutation.Count =  No.mutations.per.sample,
	Mutation.family.Count = No.fammily.mutations.per.sample,
	Mutation.homo.Count =  No.homo.mutations.per.sample,
	Mutation.hetero.Count =  No.hetero.mutations.per.sample,
	SBS.Count = No.sbs.per.sample,
	INDEL.Count = No.indel.per.sample,
	Insertion.Count = No.insertion.per.sample,
	Deletion.Count = No.deletion.per.sample,
	kakudai.group = Group
)
mutation.count.frame$Family <- factor(mutation.count.frame$Family, levels=c("A01","A02","A03","A11","A12","A13","A21","A22","A23","A31","A32","A33"))

write.csv(mutation.count.frame, "No.mutations.summary.csv",quote=F, row.names=F)
```

## statistical analyses of the number of each type of mutation

### statistical modeling of the total number of mutations (SBSs + INDELs)

```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLM with a negative binominal distribution
glm.nb.total.mutation <- glm.nb(mutation.count.frame$Mutation.Count ~ mutation.count.frame$Gray)
print(summary(glm.nb.total.mutation))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLMM with a negative binominal distribution
glmer.nb.total.mutation <- glmer.nb(Mutation.Count ~ Gray + (1|Family), data=mutation.count.frame)
print(summary(glmer.nb.total.mutation))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLM with a poisson distribution
glm.poisson.total.mutation <- glm(mutation.count.frame$Mutation.Count ~ mutation.count.frame$Gray, family = poisson)
print(summary(glm.poisson.total.mutation))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLMM with a poisson distribution
glmer.poisson.total.mutation <- glmer(Mutation.Count ~ Gray + (1|Family), family=poisson, data=mutation.count.frame)
print(summary(glmer.poisson.total.mutation))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# Non-lenear second polynominal model
nls.2nd.total.mutation <- nls(mutation.count.frame$Mutation.Count ~　a+b*mutation.count.frame$Gray+c*(mutation.count.frame$Gray)^2, data= mutation.count.frame, start=c(a=1, b=1, c=1),trace=T)
print(summary(nls.2nd.total.mutation))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
model.AICs.total.mutation <- AIC(glm.nb.total.mutation, glmer.nb.total.mutation,glm.poisson.total.mutation, glmer.poisson.total.mutation, nls.2nd.total.mutation)
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# Overdespersion test: poisson vs negative binomial
overdispertion.test.total.mutation <- dispersiontest(glm.poisson.total.mutation)
print(overdispertion.test.total.mutation)
odTest(glm.nb.total.mutation)
```

### statistical modeling of the number of SBS mutations

```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLM with a negative binomial distribution
glm.nb.sbs <- glm.nb(mutation.count.frame$SBS.Count ~ mutation.count.frame$Gray)
print(summary(glm.nb.sbs))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLMM with a negative binomial distribution
glmer.nb.sbs <- glmer.nb(SBS.Count ~ Gray + (1|Family), data=mutation.count.frame)
print(summary(glmer.nb.sbs))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLM with a poisson distribution
glm.poisson.sbs <- glm(mutation.count.frame$SBS.Count ~ mutation.count.frame$Gray, family = poisson)
print(summary(glm.poisson.sbs))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# GLMM with a poisson distribution
glmer.poisson.sbs <- glmer(SBS.Count ~ Gray + (1|Family), family=poisson, data=mutation.count.frame)
print(summary(glmer.poisson.sbs))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
# Non-lenear second polynominal model
nls.2nd.sbs <- nls(mutation.count.frame$SBS.Count ~　a+b*mutation.count.frame$Gray+c*(mutation.count.frame$Gray)^2, data= mutation.count.frame, start=c(a=1, b=1, c=1),trace=T)
print(summary(nls.2nd.sbs))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
AIC(glm.nb.sbs, glmer.nb.sbs, glm.poisson.sbs, glmer.poisson.sbs, nls.2nd.sbs)
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("Overdespersion test: poisson vs negative binomial")
overdispertion.test.sbs <- dispersiontest(glm.poisson.sbs)
print(overdispertion.test.sbs)
odTest(glm.nb.sbs)
```


### statistical modeling of the number of INDEL mutations

```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLM with a negative binomial distribution ***\n")
glm.nb.indel <- glm.nb(mutation.count.frame$INDEL.Count ~ mutation.count.frame$Gray)
print(summary(glm.nb.indel))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a negative binomial distribution ***\n")
glmer.nb.indel <- glmer.nb(INDEL.Count ~ Gray + (1|Family), data=mutation.count.frame)
print(summary(glmer.nb.indel))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLM with a poisson distribution ***\n")
glm.poisson.indel <- glm(mutation.count.frame$INDEL.Count ~ mutation.count.frame$Gray, family = poisson)
print(summary(glm.poisson.indel))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a poisson distribution ***\n")
glmer.poisson.indel <- glmer(INDEL.Count ~ Gray + (1|Family), family=poisson, data=mutation.count.frame)
print(summary(glmer.poisson.indel))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("Non-lenear second polynominal model\n")
nls.2nd.indel <- nls(mutation.count.frame$INDEL.Count ~　a+b*mutation.count.frame$Gray+c*(mutation.count.frame$Gray)^2, data= mutation.count.frame, start=c(a=1, b=1, c=1),trace=T)
print(summary(nls.2nd.indel))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
AIC(glm.nb.indel, glmer.nb.indel, glm.poisson.indel, glmer.poisson.indel, nls.2nd.indel)
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
overdispertion.test.indel <- dispersiontest(glm.poisson.indel)
print(overdispertion.test.indel)
odTest(glm.nb.indel)
```

### statistical modeling of the number of deletion mutations

```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a negative binomial distribution ***\n")
glm.nb.deletion <- glm.nb(Deletion.Count ~ Gray, data=mutation.count.frame)
print(summary(glm.nb.deletion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a negative binomial distribution ***\n")
glmer.nb.deletion <- glmer.nb(Deletion.Count ~ Gray + (1|Family), data=mutation.count.frame)
print(summary(glmer.nb.deletion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLM with a poisson distribution ***\n")
glm.poisson.deletion <- glm(Deletion.Count ~ Gray, family = poisson, data=mutation.count.frame)
print(summary(glm.poisson.deletion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a poisson distribution ***\n")
glmer.poisson.deletion <- glmer(Deletion.Count ~ Gray + (1|Family), family=poisson, data=mutation.count.frame)
print(summary(glmer.poisson.deletion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("Non-lenear second polynominal model\n")
nls.2nd.deletion <- nls(Deletion.Count ~　a+b*Gray+c*Gray^2, data= mutation.count.frame, start=c(a=1, b=1, c=1),trace=T)
print(summary(nls.2nd.deletion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
AIC(glm.nb.deletion, glmer.nb.deletion, glm.poisson.deletion, glmer.poisson.deletion, nls.2nd.deletion)
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
overdispertion.test.deletion <- dispersiontest(glm.poisson.deletion)
print(overdispertion.test.deletion)
odTest(glm.nb.deletion)
```

### statistical modeling of the number of insertion mutations

```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLM with a negative binomial distribution ***\n")
glm.nb.insertion <- glm.nb(Insertion.Count ~ Gray,data= mutation.count.frame)
print(summary(glm.nb.insertion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a negative binomial distribution ***\n")
glmer.nb.insertion <- glmer.nb(Insertion.Count ~ Gray + (1|Family), data=mutation.count.frame)
print(summary(glmer.nb.insertion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLM with a poisson distribution ***\n")
glm.poisson.insertion <- glm(Insertion.Count ~ Gray, family = poisson, data=mutation.count.frame)
print(summary(glm.poisson.insertion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("*** GLMM with a poisson distribution ***\n")
glmer.poisson.insertion <- glmer(Insertion.Count ~ Gray + (1|Family), family=poisson, data=mutation.count.frame)
print(summary(glmer.poisson.insertion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
cat("Non-lenear second polynominal model\n")
nls.2nd.insertion <- nls(Insertion.Count ~　a+b*Gray+c*Gray^2, data= mutation.count.frame, start=c(a=1, b=1, c=1),trace=T)
print(summary(nls.2nd.insertion))
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
AIC(glm.nb.insertion, glmer.nb.insertion, glm.poisson.insertion, glmer.poisson.insertion, nls.2nd.insertion)
```
```{r message = FALSE, warning = FALSE, echo = TRUE}
overdispertion.test.insertion <- dispersiontest(glm.poisson.insertion)
print(overdispertion.test.insertion)
odTest(glm.nb.insertion)
```

### Plotting the relationship between the number of each type of mutaion and radiation

```{r message = FALSE, warning = FALSE, echo = TRUE}
sbs.indel.color <- "mediumpurple"
indel.color <- "mediumblue"
black.color <- "black"
samon.color <- rgb(1,0.75,0.85)

chairo.color <- rgb(128/255,64/255,0/255)
aka.color <- rgb(255/255,75/255,0/255)
total.color <- chairo.color

midori.color <- rgb(3/255,175/255,122/255)
pink.color <- rgb(255/255,128/255,130/255)
sbs.color <-pink.color
deletion.color <- ao.color <- rgb(0/255,90/255,255/255)
sora.color <- rgb(77/255,196/255,255/255)
insertion.color <- sora.color
orange.col <- rgb(246/255,170/255,0/255)
murasaki.col <- rgb(153/255,0/255,153/255)

gg.plot.total.mutation <- ggplot2::ggplot() +
	xlab("Radiation dose (Gy/d)") +
	ylab("No. mutations") +
	theme(axis.title.x = element_text(size=16), axis.title.y = element_text(size=16),
		axis.text.x = element_text(size=16),axis.text.y = element_text(size=16)) +
	geom_count(data=mutation.count.frame,aes(x=Gray, y= Mutation.Count), pch=1, col=total.color) +
	geom_smooth(data=mutation.count.frame,aes(x=Gray, y= Mutation.Count), method = lm, formula = y ~ exp(glmer.nb.total.mutation@beta[1] + glmer.nb.total.mutation@beta[2]*x), se =FALSE,col=total.color,lwd=0.8) + scale_size_continuous(breaks = seq(1,9,1)) +
	geom_count(data=mutation.count.frame,aes(x=Gray, y= SBS.Count), pch=2, col=sbs.color) +　scale_size_continuous(breaks = seq(1,9,1)) +
	geom_smooth(data=mutation.count.frame,aes(x=Gray, y= SBS.Count), method = lm, formula = y ~ exp(glmer.nb.sbs@beta[1] + glmer.nb.sbs@beta[2]*x), se =FALSE,col=sbs.color, lwd=0.6) + scale_size_continuous(breaks = seq(1,9,1)) +
	geom_count(data=mutation.count.frame,aes(x=Gray, y= Insertion.Count), pch=3, col=insertion.color) +　scale_size_continuous(breaks = seq(1,9,1)) +
	geom_smooth(data=mutation.count.frame,aes(x=Gray, y= Insertion.Count), method = glm, method.args = list(family = "poisson"), se =FALSE, col=insertion.color,lwd=1,lty="dotted") +
	geom_count(data=mutation.count.frame,aes(x=Gray, y= Deletion.Count), pch=4, col=deletion.color) +　scale_size_continuous(breaks = seq(1,9,1)) +
	geom_smooth(data=mutation.count.frame,aes(x=Gray, y= Deletion.Count), method = MASS::glm.nb, se =FALSE, col=deletion.color, lwd=0.6)

plot(gg.plot.total.mutation)
```
